### 2010-12-06 report/report.tex
edited future work, etc.

\edit{also describe parameterized motion model}

We implemented and tested 8 different learning strategies:
\begin{itemize}
\item \emph{Uniform random hill climbing}: Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing it completely 
  randomly in UniformStrategy(). Then evaluates this neighbor by running 
  the robot with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
\item \emph{Gaussian random hill climbing}: Creates a random neighbor by
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
\item \emph{N-dimensional policy gradient descent}: Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score for
  each parameter and adjusts the base policy according to the estimated
  gradient.
\item \emph{Random}: Randomly generates policies in the range of the motion
representation.
\item \emph{Simplex (Nelder-Mead) Method}: Creates a simplex with 6 vertices and tests the fitness of each vertex. The worst vertex is reflected over the centroid. If the reflected point is better than the second worst point and worse than the best point, then the reflected point replaces the worst. If the reflected point is better than the best point, the simplex is expanded in the direction of the reflected point. The better of the reflected and the expanded point replaces the worst point. If the reflected point is worse than the second worst point, then the simplex is contracted away from the reflected point. If the contracted point is better than the reflected point, the contracted point replaces the worst point. If the contracted point is worse than the reflected point, the entire simplex is shrunk \cite{NMWebsite}.
\item \emph{Linear regression}: To initialize, chooses five random points
and trains on them using least-squares. Then in a loop, takes a fixed-size
step in the direction of the gradient, and retrains on all points so far.
\item \emph{SVM regression}
\item \emph{Evolutionary Neural Network (HyperNEAT)\cite{2}}
\end{itemize}

@@

\item \code{MotionModel} abstract base class: Several functions exist,
  but none are within a class framework. ... ??? ... \code{SineModel}
  classes: Commands motors to positions based on a sine wave, creating
  a periodic pattern. Parameters are: amplitude, wavelength, scale
  inner vs outer motors, scale left vs right motors, scale back vs
  front motors. Currently a function, not a class. ... ??? ... THere
  are also other motion models... Other derived motion model classes:
  Several versions of a SineModel exist, each with different
  parameters, though solely as functions.

@@

\edit{Intro sentence here...}

\begin{itemize}
\item More runs and/or longer runs
\item Different motion representations
\item Evolutionary algorithms/HyperNEAT\cite{2}
\item Learning how to turn
\item Open sourcing code for others to extend
\end{itemize}

>>>>

We have a parameterized motion model that commands motors to positions
based on a sine wave, creating a periodic pattern. Parameters are: 
amplitude, wavelength, scale inner vs outer motors, scale left vs right 
motors, scale back vs front motors. Each strategy below attempts to choose
the best possible parameters for this motion model.

We implemented and tested 8 different learning strategies:
\begin{itemize}
\item \emph{Uniform random hill climbing}: Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing it completely 
  randomly in UniformStrategy(). Then evaluates this neighbor by running 
  the robot with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
\item \emph{Gaussian random hill climbing}: Creates a random neighbor by
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
\item \emph{N-dimensional policy gradient descent}: Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score for
  each parameter and adjusts the base policy according to the estimated
  gradient.
\item \emph{Random}: Randomly generates parameter vector in the allowable
  range. This strategy is used only as base line.
\item \emph{Simplex (Nelder-Mead) Method}: Creates a simplex with 6 vertices and tests the fitness of each vertex. The worst vertex is reflected over the centroid. If the reflected point is better than the second worst point and worse than the best point, then the reflected point replaces the worst. If the reflected point is better than the best point, the simplex is expanded in the direction of the reflected point. The better of the reflected and the expanded point replaces the worst point. If the reflected point is worse than the second worst point, then the simplex is contracted away from the reflected point. If the contracted point is better than the reflected point, the contracted point replaces the worst point. If the contracted point is worse than the reflected point, the entire simplex is shrunk \cite{NMWebsite}.
\item \emph{Linear regression}: To initialize, chooses five random points
and trains on them using least-squares. Then in a loop, takes a fixed-size
step in the direction of the gradient, and retrains on all points so far.
\item \emph{SVM regression}
\item \emph{Evolutionary Neural Network (HyperNEAT)\cite{2}}
\end{itemize}

@@

\item \code{MotionModel} abstract base class: Several functions exist,
  but none are within a class framework. ... ??? ...

  \begin{itemize} 
  \item \code{SineModel}
  classes: Commands motors to positions based on a sine wave, creating
  a periodic pattern. Parameters are: amplitude, wavelength, scale
  inner vs outer motors, scale left vs right motors, scale back vs
  front motors. Currently a function, not a class. ... ??? ... There
  are also other motion models...

  \item Other derived motion model classes:
  Several versions of a SineModel exist, each with different
  parameters, though solely as functions.
  \end{itemize}

@@

\edit{Intro sentence here...}
There are several additions we would make to flesh out our project. First,
the error margins for our runs was quite large, so reducing them would lead
to more conclusive data. It would also be insightful to run our algorithms
on different motion models to get a better idea of how well different
algorithms perform overall, and not just for our current motion model. We
also intend to experiment more with evolutionary algorithms/HyperNEAT. 
Some parameter vectors resulted in the robot turning, as opposed to it
walking long distances. This could be an interesting learning goal in
future projects. To these ends, we propose the following additions
and enhancements:

\begin{itemize}
\item More runs and/or longer runs
\item Different motion representations
\item Evolutionary algorithms/HyperNEAT\cite{2}
\item Learning how to turn
\end{itemize}
